---
title: "hw3"
output: pdf_document
---

```{r}
#Question 1
mu <- read.table("maybe_uniform.txt", header = FALSE)
c1 <- c(mu$V1,mu$V2,mu$V3,mu$V4,mu$V5)
hist(c1)

```

```{r}
ks.test(c1,"punif")
```

```{r}
x <- seq(0, 1, by = 0.0001)
fx <- ifelse(x >0 & x <= 1/2, 2/3,
ifelse(x >1/2 & x < 1, 1/2, 0))

plot(x, fx)
```

```{r}
ks.test(mu,x)
```

According to the ks.test result, the p-value is larger than 0.05 which means data is uniformly distributed. Since D-value for fx is also bigger, which means Uniform would be better.

```{r}
#Question 2
table2 <- read.table("maybe_normal.txt")
c2 <- c(table2$V1,table2$V2,table2$V3,table2$V4,table2$V5)

set.seed(2000)
n1 <- rnorm(50, mean = 26, sd = 2)
qqplot(c2,n1)
hist(c2)
hist(n1)

ks.test(c2,n1)
```
The data might generate by normal distribution, base on the result.

```{r}
#Question 3

same1 <- read.table("maybe_same_1.txt")
same2 <- read.table("maybe_same_2.txt")
s1 <- c(same1$V1,same1$V2,same1$V3,same1$V4,same1$V5)
s2 <- c(same2$V1,same2$V2,same2$V3,same2$V4)
ks.test(s1, s2)
```

```{r}
ks.test(s1+2,s2)
```

For ks.test(s1,s2), p-value is bigger than 0.05, fail to reject null hypothesis. s1,s2 from same distribution. For ks.test(s1+2,s2), p-value is very small, reject null hypothesis: s1+2,s2 not from same distribution.

```{r}
rds1 <- readRDS("norm_sample.Rdata")
ecdf1 <- ecdf(rds1)
plot(ecdf1)
```

```{r}
a <- rnorm(25,0,1)
ks.test(rds1,a)

```

```{r}
dfns <- as.data.frame(rds1)
dfns$dif <- abs(ecdf1(rds1) - pnorm(rds1))
dstat <- max(dfns$dif)

dstat

ks.test(rds1,"pnorm")

```

```{r}
# Question 5
fijiquakes <- read.table("fijiquakes(1).dat", header = TRUE)
faithful <- read.table("faithful(1).dat", header = TRUE, skip = 20)

library(sfsmisc)
ecdf.ksCI(fijiquakes$mag)
ecdf.ksCI(faithful$waiting)

```

```{r}
amount <- sum( (fijiquakes$mag <= 4.9) & (fijiquakes$mag > 4.3))
library(Hmisc)
binconf(amount, alpha = 0.05, length(fijiquakes$mag), method=c("wilson","exact","asymptotic","all"))

mean(faithful$waiting)
median(faithful$waiting)


```


